An agent-based model for city networks based on interactions between firms

### 2019-10-16 main.tex
Update on Overleaf.
.

    \item The ``geopolitical/sociocultural'' distance remains abstract and should be parametrized (see setup below) and estimated in the data-driven setting.
    \item \textcolor{red} TODO the path dependency $w_{ij}$ could (or should ?) be decomposed into in/out degree for origin and destination ? (then stronger self-reinforcment effect)
    \end{itemize}
\end{enumerate}

@@

>>>>

    \item The ``geopolitical/sociocultural'' distance remains abstract and should be parametrized (see setup below) and estimated in the data-driven setting.
    \item %\textcolor{red}
    TODO the path dependency $w_{ij}$ could (or should ?) be decomposed into in/out degree for origin and destination ? (then stronger self-reinforcment effect)
    \end{itemize}
\end{enumerate}

@@

\subsubsection{Real data setup}

Data sources:
\begin{itemize}
	\item ORBIS database for company links
	\item GHS UCDB for GDP of urban built-up areas
	\item Functional urban areas (JRC-EC) for consistent ontology and spatial join between the different sources
\end{itemize}

If the links are ``complete'' within Europe, the model (i) can be initialized at $t_0$ with the network corresponding to the first date in the dataset; (ii) adjustment error is computed on the later dates.

More probably, we may have to work on an extract of the ORBiS database including only links from and to UK-based companies
